candidate genes

### 2019-12-15 analysis/10_specificgenes.Rmd
better colors

x <- correlate(counts)
rplot(x)  + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(subtitletitle = "inc.d9 to inc.d17")

x %>% network_plot.cor_df(min_cor = .6, colors = c("#67a9cf", "white", "#ef8a62")) + 
  labs(subtitletitle = "inc.d9 to inc.d17")

@@

x <- correlate(counts)
rplot(x)  + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(subtitle = "bldg to lay")

x %>% network_plot.cor_df(min_cor = .6, colors = c("#67a9cf", "white", "#ef8a62")) + 
  labs(subtitle = "bldg to lay")

@@

x <- correlate(counts)
rplot(x) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(subtitle = "lay to inc.d3")

x %>% network_plot.cor_df(min_cor = .6, colors = c("#67a9cf", "white", "#ef8a62"))  + 
  labs(subtitle = "lay to inc.d3")

@@

x <- correlate(counts)
fashion(x)
rplot(x) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(subtitle = "hatch to n5")

x %>% network_plot.cor_df(min_cor = .6, colors = c("#67a9cf", "white", "#ef8a62"))  + 
  labs(subtitle = "hatch to n5")

>>>>

@@

x <- correlate(counts)
rplot(x, colors = c("skyblue1", "white", "indianred2"))  + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(subtitle = "bldg to lay")

x %>% network_plot.cor_df(min_cor = .6 , colors = c("skyblue1", "white", "indianred2")) + 
  labs(subtitle = "bldg to lay")

@@

x <- correlate(counts)
rplot(x, colors = c("skyblue1", "white", "indianred2")) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(subtitle = "lay to inc.d3")

x %>% network_plot.cor_df(min_cor = .6 , colors = c("skyblue1", "white", "indianred2"))  + 
  labs(subtitle = "lay to inc.d3")

x <- correlate(counts)
rplot(x, colors = c("skyblue1", "white", "indianred2"))  + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(subtitletitle = "inc.d9 to inc.d17")

x %>% network_plot.cor_df(min_cor = .6 , colors = c("skyblue1", "white", "indianred2")) + 
  labs(subtitletitle = "inc.d9 to inc.d17")

@@

x <- correlate(counts)
rplot(x,  colors = c("skyblue1", "white", "indianred2")) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(subtitle = "hatch to n5")

x %>% network_plot.cor_df(min_cor = .6, colors = c("skyblue1", "white", "indianred2"))  + 
  labs(subtitle = "hatch to n5")
